---
title: "The Role Of *NRN1* Gene In Schizophrenia: Analysis Of Its Genetic Variability In Cortical Thickness"
author: "Enric Garcia Torrents"
date: "5/20/2020"
output: html_document
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(shiny)
library(ggplot2)
library(lemon)
library(tidyverse)

### Load workspace

load("workspace.RData")

### Soluciona el problema de la consistència dels colors
### Create a custom color scale

myColors <- c("red", "magenta", "blue", "grey")
names(myColors) <- levels(affected_DF$Sig)
# colScale <- scale_colour_manual(name = "Sig", values = myColors)

### Create new dataframe for interactive plots

affected_DF['Category']='Affected'
unaffected_DF['Category']='Unaffected'
intragroup_DF <- rbind(affected_DF, unaffected_DF)

```

<br>

## Intragroup significance levels:
 
```{r heatmaps intragroup, echo=FALSE}

inputPanel(

selectInput("Category", label = "Group to visualize:", choices = c("Affected", "Unaffected"), selected = "Affected"),

selectInput("Hemispheres", label = "Hemisphere to visualize:", choices = c("Right", "Left", "Total"), selected = "Total")

)

renderPlot({

selection <- intragroup_DF %>% filter(Category == input$Category)

selection %>% filter(Hemisphere == input$Hemispheres) %>% ggplot(selection, mapping = aes(x = factor(SNP, levels=c("rs2208870", "rs12333117", "rs582186", "rs645649", "rs582262", "rs3763180", "rs10484320", "rs4960155", "rs9379002", "rs9405890", "rs1475157")), y = reorder(factor(ID), desc(factor(ID))), fill = Sig)) +  geom_tile() + facet_rep_grid(factor(Hemisphere, levels=c("Right", "Left", "Total")) ~ TEST, scales = "free", repeat.tick.labels = "y") + theme(legend.key.size = unit(0.5,"line"), legend.title = element_text(color = "black", size = 8, face="bold"), legend.text = element_text(color = "black", size = 8), legend.position="bottom", axis.text.x = element_text(size = 7, angle = 90), axis.text.y = element_text(size = 5)) + ylab("Phenotype") + xlab("SNP") + ggtitle('Heatmap of significant levels per test and SNP; intragroup') + theme(plot.title = element_text(size=11)) + scale_fill_manual(name = "Significance level: ", values = myColors)
  
  })
```

## All individuals significance levels:

```{r heatmaps all, echo=FALSE}

inputPanel(

selectInput("Hemispheres_ALL", label = "Hemisphere to visualize:", choices = c("Right", "Left", "Total"), selected = "Total")

)

renderPlot({

# linear_ALL_interaction_DF %>% filter(Hemisphere == input$Hemispheres) %>%
    
linear_ALL_interaction_DF %>% filter(Hemisphere == input$Hemispheres_ALL) %>% ggplot(linear_ALL_interaction_DF[linear_ALL_interaction_DF$TEST == "ADDxCOV8",], mapping = aes(x = factor(SNP, levels=c("rs2208870", "rs12333117", "rs582186", "rs645649", "rs582262", "rs3763180", "rs10484320", "rs4960155", "rs9379002", "rs9405890", "rs1475157")), y = reorder(factor(ID), desc(factor(ID))), fill = Sig)) +  geom_tile() + facet_rep_grid(factor(Hemisphere, levels=c("Right", "Left", "Total")) ~ TEST, scales = "free", repeat.tick.labels = "y") + theme(legend.key.size = unit(0.5,"line"), legend.title = element_text(color = "black", size = 8, face="bold"), legend.text = element_text(color = "black", size = 8), legend.position="bottom", axis.text.x = element_text(size = 7, angle = 90), axis.text.y = element_text(size = 5)) + ylab("Phenotype") + xlab("SNPs") + ggtitle('Heatmap of significant levels per test and SNP; all individuals') + theme(plot.title = element_text(size=11)) + scale_fill_manual(name = "Significance level: ", values = myColors)

  })
```


## False Discovery Rates (FDR):

```{r FDR, echo=FALSE}

inputPanel(

selectInput("FDR", label = "FDR to visualize:", choices = c("All individuals", "Affected individuals", "Affected, dominant","Affected, recessive", "Unaffected individuals", "Unaffected, dominant", "Unaffected, recessive"), selected = "All individuals")

)

renderPlot({

first.plot <- switch(input$FDR, 
                     "All individuals" = FDR_Plot_All_Individuals,
                     "Affected individuals" = FDR_Plot_affected_Individuals,
                     "Affected, dominant" = FDR_Plot_affected_Individuals_DOM,
                     "Affected, recessive" = FDR_Plot_affected_Individuals_REC,
                     "Unaffected individuals" = FDR_Plot_unaffected_Individuals,
                     "Unaffected, dominant" = FDR_Plot_unaffected_Individuals_DOM,
                     "Unaffected, recessive" = FDR_Plot_unaffected_Individuals_REC
                     )

first.plot

  })
```
BH = Benjamini–Hochberg method


## Covariates:
 
**1**	Estimated total intracranial volume  
**2**	Age at the time of the MRI  
**3**	Age at debut of disease  
**4**	Sex  
**5**	TAP-E    
**6**	AP EQP total  
**7**	AP EQP total Andreasen  
**8**	Diagnostic (patient or control)

## Brain regions IDs:

<table align=center style="width: 100%"><tr><td>
#### Right Hemisphere
</td><td>
#### Left Hemisphere
</td><td>
#### Total
</td></tr><tr><td>
**1** Bankssts  
**2** Caudalanteriorcingulate  
**3** Caudalmiddlefrontal  
**4** Cuneus  
**5** Entorhinal  
**6** Fusiform  
**7** Inferiorparietal  
**8** Inferiortemporal  
**9** Isthmuscingulate  
**10** Lateraloccipital  
**11** Lateralorbitofrontal  
**12** Lingual  
**13** Medialorbitofrontal  
**14** Middletemporal  
**15** Parahippocampal  
**16** Paracentral  
**17** Parsopercularis  
**18** Parsorbitalis  
**19** Parstriangularis  
**20** Pericalcarine  
**21** Postcentral  
**22** Posteriorcingulate  
**23** Precentral  
**24** Precuneus  
**25** Rostralanteriorcingulate  
**26** Rostralmiddlefrontal  
**27** Superiorfrontal  
**28** Superiorparietal  
**29** Superiortemporal  
**30** Supramarginal  
**31** Frontalpole  
**32** Temporalpole  
**33** Transversetemporal  
**34** Insula  
**35** Meanthickness
</td><td>
**36** Bankssts  
**37** Caudalanteriorcingulate  
**38** Caudalmiddlefrontal  
**39** Cuneus  
**40** Entorhinal  
**41** Fusiform  
**42** Inferiorparietal  
**43** Inferiortemporal  
**44** Isthmuscingulate  
**45** Lateraloccipital  
**46** Lateralorbitofrontal  
**47** Lingual  
**48** Medialorbitofrontal  
**49** Middletemporal  
**50** Parahippocampal  
**51** Paracentral  
**52** Parsopercularis  
**53** Parsorbitalis  
**54** Parstriangularis  
**55** Pericalcarine  
**56** Postcentral  
**57** Posteriorcingulate  
**58** Precentral  
**59** Precuneus  
**60** Rostralanteriorcingulate  
**61** Rostralmiddlefrontal  
**62** Superiorfrontal  
**63** Superiorparietal  
**64** Superiortemporal  
**65** Supramarginal  
**66** Frontalpole  
**67** Temporalpole  
**68** Transversetemporal  
**69** Insula  
**70** Meanthickness
</td><td>
**71** Bankssts  
**72** Caudalanteriorcingulate  
**73** Caudalmiddlefrontal  
**74** Cuneus  
**75** Entorhinal  
**76** Fusiform  
**77** Inferiorparietal  
**78** Inferiortemporal  
**79** Isthmuscingulate  
**80** Lateraloccipital  
**81** Lateralorbitofrontal  
**82** Lingual  
**83** Medialorbitofrontal  
**84** Middletemporal  
**85** Parahippocampal  
**86** Paracentral  
**87** Parsopercularis  
**88** Parsorbitalis  
**89** Parstriangularis  
**90** Pericalcarine  
**91** Postcentral  
**92** Posteriorcingulate  
**93** Precentral  
**94** Precuneus  
**95** Rostralanteriorcingulate  
**96** Rostralmiddlefrontal  
**97** Superiorfrontal  
**98** Superiorparietal  
**99** Superiortemporal  
**100** Supramarginal  
**101** Frontalpole  
**102** Temporalpole  
**103** Transversetemporal  
**104** Insula  
**105** Meanthickness
</td></tr></table>

<br><br>
